What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
minor algo1 fix
update scalability

\begin{algorithm}[h!]
    \caption{reduce\_dfa}
    \begin{algorithmic}
        \Require ($G, v$), a DFA with state $v$ that is not initial or final
        \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
        \For{ every $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ }
            \If {$v$ has a self-edge  $v\xrightarrow{r_\mathrm{loop}}v$}
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in} r_\mathrm{loop}* r_\mathrm{out}} w$
            \Else
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in}  r_\mathrm{out}} w$
            \EndIf
        \EndFor
        %\State \Return the reduced graph $G$
    \end{algorithmic}
\end{algorithm}

@@

\paragraph{Scalability}
We measure the scalability of our tool by running it against a set of scalable \ltl\ formulas. We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter \cite{RV10}. As $n$ gets larger, the \ltl\ formula used to encode the $n$-bit counter scales in size, but it remains practical. The result is shown in \cref{fig:scalability}.
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.7]{img/scale.png}
    \caption{Scalability measured with binary counter examples from Rozier and Vardi \cite{RV10}}
    \label{fig:scalability}
\end{figure}

>>>>

\begin{algorithm}[h!]
    \caption{reduce\_dfa}
    \begin{algorithmic}
        \Require ($G, v$), a DFA with state $v$ that is not initial or final
        \Ensure Deletes state $v$ from $G$ while ensuring the same language is recognized
        \For{ every $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ }
            \If {$v$ has a self-edge  $v\xrightarrow{r_\mathrm{loop}}v$}
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in} r_\mathrm{loop}* r_\mathrm{out}} w$
            \Else
                \State replace edges $u\xrightarrow{r_\mathrm{in}} v, v \xrightarrow{r_\mathrm{out}} w$ with $u \xrightarrow{r_\mathrm{in}  r_\mathrm{out}} w$
            \EndIf
        \EndFor
	\State delete node $v$ from $G$
        %\State \Return the reduced graph $G$
    \end{algorithmic}
\end{algorithm}

@@

\paragraph{Scalability}
We measure the scalability of our tool by running it against a set of scalable \ltl\ formulas. We define a scalable \ltl\ formula as one that describes an $n$-bit number using a binary counter \cite{RV10}. As $n$ gets larger, the \ltl\ formula used to encode the $n$-bit counter scales in size, but it remains practical. The result is shown in \cref{fig:scalability}. In this analysis, the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi \cite{RV10}.

In \cref{fig:scalability}, the x-axis ranges from $1$ to $6$, after which point it hits the $30$ seconds timeout we set, as the timeline length grows exponentially fast.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.7]{img/scale.png}
    \caption{Scalability measured with binary counter examples from Rozier and Vardi \cite{RV10}}
    \label{fig:scalability}
\end{figure}
